Thesis outline

### 2017-07-19 KellyDouglass/Thesis/Thesis_sections/smallScaleEnvironment.tex
Updated text in small scale environment chapter

% Small-scale environment - what has been done so far?
In conjunction with the large-scale environment, the small-scale environment 
($\sim$1 \hMpc) has also been found to influence a galaxy's evolution.  A 
well-established morphology-density relation exists \citep{Dressler80}, where 
the fraction of late-type galaxies is inversely proportional to the local 
density.  \cite{Ellison09} determined that a galaxy's local environment 
influences a galaxy's evolution more than its large-scale environment.  
Likewise, \cite{Rupke08} concluded that interacting galaxies have suppressed 
metallicities, because interactions induce flows of hydrogen.  \cite{Park09} 
found that, for galaxies with $M_r < -19$, galaxy interactions out to the virial 
radius of the nearest neighbor influence the evolution of the target galaxy.  
Along with \cite{Park07}, they determine that the large-scale environment has a 
minimal effect on the evolution of a galaxy once the luminosity and morphology 
are taken into account.

@@

We employ two different spatial metrics to determine the best way to locate a 
galaxy's nearest neighbor.  We set a maximum velocity separation of 300 km/s 
between a galaxy and its nearest neighbor to capture the majority of interacting 
galaxies \citep[according to the distribution in peculiar velocity shown in][]
{Hwang10}.  Within a relative velocity $v_{rel} < 300\text{ km/s}$, we use 
either the physically closest galaxy in units of \hMpc or the galaxy within the 
smallest fraction of its virial radius; both these methods are described below 
in further detail.  The two methods result in different neighboring galaxies for 
about 40\% of our dwarf galaxy sample.

@@

A galaxy's redshift is composed of both the expansion of the universe and the 
galaxy's peculiar velocity (its motion relative to its surrounding galaxies and 
environment).  Known as the ``Finger of God'' effect, the peculiar velocity 
causes galaxy groups and clusters to appear extended along the line of sight 
when using redshift as a distance measurement.  When we calculate distances on 
large scales, the peculiar velocity is negligible.  However, when we study the 
distance between two objects in the universe on a small scale (within a few 
\hMpc), the peculiar velocity dominates.  The relative velocity $v_{rel}$ 
between galaxies $a$ and $b$ is defined as
\begin{equation}
    v_{rel} = |z_a - z_b|c
\end{equation}
where $z$ is the redshift.  We require all 
neighbors to have a maximum relative velocity $v_{rel} < 300\text{ km/s}$, as we 
believe those outside this range will have minimal influence on the target 
galaxy's evolution.  We show in Sec. \ref{sec:selection_effects} that our 
results are insensitive to this value.

@@

The projected distance between two galaxies is found by projecting the two 
galaxies onto a sphere of radius $\bar{r}$, where $\bar{r}$ is the average 
distance from Earth of the two galaxies.  This assumes that two galaxies which 
are gravitationally bound are in a system where the relative velocity between us 
and it is 0 and that $\bar{r}$ is the distance to the center of the system.  For 
redshifts $z \ll 1$, we can approximate the distance to the system is as
\begin{equation}
    \bar{r} = \frac{\bar{z}c}{H_0}
\end{equation}
where $\bar{z}$ is the average redshift of the two galaxies, $c$ is the speed of 
light, and $H_0$ is the Hubble constant.  Each galaxy's right ascension (RA) and 
declination (dec.) are converted to Cartesian coordinates to find their sky 
separation.

@@

\cite{Choi07} find that the velocity dispersion of a galaxy depends on its 
morphological type, where $\sqrt{2}\sigma_{late} \approx \sigma_{early}$.  In 
terms of the velocity dispersion, the kinetic energy of a galaxy 
$K = 3/2 \sigma^2$.  Its gravitational potential energy $U = 3GM/5R$.  
Therefore, the virial theorem shows us that
\begin{align}
    3\sigma^2 \simeq \frac{3}{5} \frac{GM}{R}\nonumber \\
    M \simeq \frac{5\sigma^2 R}{G}
\end{align}
With $\gamma \equiv M/L$, at a fixed luminosity and virial radius we see that
\begin{equation}
    \gamma_{late} \simeq \frac{5\sigma_{late}^2 R}{GL} \qquad \gamma_{early} \simeq \frac{5\sigma_{early}^2 R}{GL}
\end{equation}
Taking the ratio of the two mass-to-light ratios and using the relation between 
the velocity dispersions found by \cite{Choi07}, we find that the mass-to-light 
ratio depends on the galaxy's morphology type: $\gamma_{early} = 2\gamma_{late}$.

\cite{Hwang10} defines $200\rho_c = 740\bar{\rho}$, where 
$\bar{\rho} = (0.0223\pm 0.0005)(\gamma_{late}L_{-20})(\text{\hMpc})^3$.  We can 
then rewrite Eqn. \ref{eqn:r_vir} as
\begin{equation}
    r_{vir} = \left( \frac{3}{4\times 740\times 0.0223\pi} \frac{\gamma}{\gamma_{late}} \frac{L}{L_{-20}} \right)^{1/3}
\end{equation}
where $L_{-20}$ is the luminosity of a galaxy with $M_r = -20$.  We can then use 
the virial radius to scale the distance between two galaxies as a fraction of 
the neighbor's virial radius.

@@

% SDSS
%The Sloan Digital Sky Survey Data Release 7 \citep[SDSS DR7;][]{Abazajian09} is 
%a wide-field multiband imaging and spectroscopic survey which maps approximately 
%one-quarter of the northern sky using a drift scanning technique.  Photometric 
%data in the five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$ --- is taken 
%on a dedicated 2.5m telescope at the Apache Point Observatory in New Mexico 
%\citep{Fukugita96,Gunn98}.  Galaxies with Petrosian $r$-band magnitudes 
%$m_r < 17.77$ are selected for follow-up spectroscopic analysis \citep{Lupton01,
%Strauss02}.  The galaxy colors are taken from the Korean Institute for Advanced 
%Study Value-Added Galaxy Catalog \citep[KIAS-VAGC;][]{Choi10}, which contains 
%galaxies from the SDSS DR7 main sky survey based on the New York University 
%Value-Added Galaxy Catalog Data Release 7 \citep[NYU-VAGC;][]{Blanton05}.  Total 
%star formation rates (SFR) and total specific star formation rates (sSFR) are 
%from the MPA-JHU value-added catalog\footnote{Available at 
%\url{http://www.mpa-garching.mpg.de/SDSS/DR7/}}, calculated using the technique 
%described in \cite{Brinchmann04}.  
The gas-phase chemical abundances used are from Douglass, Vogeley, and Cen 
(2017, submitted), which are calculated using the Direct $T_e$ method.  The 
galaxies' large-scale environments are based on the void catalog compiled by 
\cite{Pan12}, which is constructed from SDSS DR7 using the VoidFinder algorithm 
of \cite{Hoyle02}.  Galaxies that are located within identified voids are 
labeled as void galaxies, and those that do not fall within a void are 
designated as a wall galaxy.  The large-scale environment within 5 \hMpc of the 
edge of the main SDSS DR7 footprint cannot be described using the VoidFinder 
algorithm because the minimum diameter of a void is 10 \hMpc.  Therefore, the 
large-scale environment for galaxies within 5 \hMpc of the edge of the main 
footprint in SDSS DR7 is designated as unknown.

@@

Two galaxy samples are used in this analysis.  The largest one contains the 
11,845 dwarf galaxies spectroscopically observed in SDSS DR7.  The second sample 
contains those star-forming dwarf galaxies from the first set that have 
gas-phase chemical abundances in Douglass et al. (2017, submitted), totaling 2506 
dwarf galaxies.  While this subset of galaxies contains only star-forming 
galaxies and is not representative of all dwarf galaxies, we show in Section 
\ref{sec:selection_effects} that this does not affect our results.

@@

In addition to comparing the target galaxies to their nearest neighbor, we also 
look at the relationship between the dwarf galaxies' properties and their 
proximity to the nearest galaxy group.  We use the \emph{Mr18} Berlind group 
catalog \cite{Berlind06} as our source of groups, which is built on the galaxies 
in the NYU-VAGC. The catalog identifies groups using a friends-of-friends 
algorithm \citep{Huchra82} to connect galaxies with $M_r < -18$.

@@

The relationships between various physical parameters and the distance to the 
nearest neighbor or group for our sample of star-forming dwarf galaxies are 
shown in Figs. \ref{fig:ur}--\ref{fig:NO}.  In each of the four plots within 
each figure, we bin the galaxies in distance-space and show the average 
parameter value in each bin, to see any overall trends in the data.  We applied 
a linear regression to the data; the output of these fits are in Table 
\ref{tab:fits}.  Each of these four plots probes this distance relationship from 
a different angle.  The top left plots in Figs. \ref{fig:ur}--\ref{fig:NO} 
relate the target dwarf galaxy's parameter to the distance to its nearest 
neighbor, as defined by the the closest galaxy on the sky in \hMpc with a 
velocity difference less than 300 km/s.  The bottom left plots relate the target 
dwarf galaxy's parameter to the distance to its nearest neighbor, as defined by 
the closest galaxy on the sky in units of the virial radius of the neighbor 
galaxy with a velocity difference less than 300 km/s.  The nearest galaxy is not 
necessarily the same for these two distance measurements, as explained in Sec. 
\ref{sec:Theory_dist}.

We repeat this same analysis on the nearest groups to the target dwarf galaxy.  
The top right plots in Figs. \ref{fig:ur}--\ref{fig:NO} relate the target dwarf 
galaxy's parameter to the distance to the center of the nearest group, as 
defined as the closest group in the sky in \hMpc with a velocity difference less 
than 300 km/s.  The bottom right plots in Figs. \ref{fig:ur}--\ref{fig:NO} 
relate the target dwarf galaxy's parameter to the distance to the nearest group 
as defined by the closest group on the sky in units of the group's rms radius 
with a velocity difference of less than 300 km/s.  Groups are very rare in the 
void environment (by nature of the void environment), so the uncertainty in the 
binned values shown in these plots is much larger than in the galaxy neighbor 
plots.

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_ur}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300_group}
    \caption[$u-r$ versus distance to nearest neighbor and group]{Color ($u-r$) 
    versus distance to the nearest galaxy (on the left) and nearest group (on 
    the right).  The top panel shows the color as a function of the sky 
    separation in \hMpc between the target dwarf galaxy and the neighbor, while 
    the bottom panel shows the color as a function of the closest virial 
    neighbor.  Void galaxies are shown in red, while wall galaxies are shown in 
    black and unknown in green.  We have also included the average color for the 
    galaxies after binning by distance, to discern any finer behavior in the 
    relationships.  Linear fits to the void and wall galaxies are shown in 
    orange and blue, respectively.  It is clear that the void dwarf galaxies are 
    bluer than the wall dwarf galaxies.  The nearest galaxies appear to only 
    have some affect on the dwarf galaxy's color at separations less than 0.05 
    \hMpc, or 0.1$r_{vir}$.  %The closest group appears to have some affect on 
%    the target dwarf galaxy's color at distances less than 0.1 \hMpc to the 
%    group's center; there appears to be no relationship between a dwarf galaxy's 
%    color and its distance to the nearest group as represented by the fraction 
%    of the group's radius.}
    There appears to be no relationship between a dwarf galaxy's color and its 
    distance to the nearest group.}
    \label{fig:ur}
\end{figure}

Because of the known morphology-density relation, we expect to find that a dwarf 
galaxy's color becomes bluer as the distance to the nearest group increases, but 
we expect the dwarf galaxy's color to become bluer as the distance to the 
neighbor decreases.  Fig. \ref{fig:ur} shows very little relationship between 
the distance and color, except in the smallest distance bin.  The linear fits 
quantify this observation --- the slopes are on the order of 10$^{-3}$.  
However, within a distance of 0.05 \hMpc or 0.1$r_{vir}$, dwarf galaxies tend 
to be bluer than at further distances from their nearest neighbor.  %At distances 
%less than 0.1 \hMpc from the center of the nearest groups, the dwarf galaxies 
%are redder than average.  However, there does not appear to be any relationship 
%between a dwarf galaxy's color and its distance to the center of the nearest 
%group in units of the group's rms radius.  
There does not appear to be any relationship between a dwarf galaxy's color and 
its distance to the center of the nearest group.  
It has been well-established that 
void galaxies tend to be bluer than galaxies in denser environments 
\citep{Grogin99,Rojas04,Patiri06,vonBendaBeckmann08,Hoyle12}; this shift is 
apparent in Fig. \ref{fig:ur}, where the void dwarf galaxies are slightly bluer 
than the wall dwarf galaxies.

\subsubsection{sSFR}

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_sSFR}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_sSFR}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_sSFR}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_sSFR}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300_group}
    \caption[sSFR versus distance to nearest neighbor and group]{sSFR versus 
    distance to the nearest galaxy (on the left) and nearest group (on the 
    right).  The top panel shows the sSFR as a function of the sky separation in 
    \hMpc between the target dwarf galaxy and the neighbor, while the bottom 
    panel shows the sSFR as a function of the closest virial neighbor.  Void 
    galaxies are shown in red, while wall galaxies are shown in black and 
    unknown in green.  We have also included the average sSFR for the galaxies 
    after binning by distance, to discern any finer behavior in the 
    relationships.  Linear fits to the void and wall galaxies are shown in 
    orange and blue, respectively.  It is clear that the void dwarf galaxies 
    have higher sSFRs than the wall dwarf galaxies.  Only the neighbor galaxies 
    at separations less than 0.05 \hMpc or 0.1$r_{vir}$ appear to have some 
    affect on the dwarf galaxies' sSFR.  There appears to be no relationship 
    between a dwarf galaxy's sSFR and its distance to the nearest group.}
    \label{fig:sSFR}
\end{figure}

Following our prediction for the color-distance relations, we expect the 
sSFR to decrease with distance from the nearest neighbor and increase with 
distance from the nearest group.  We also see very little relationship between 
the distance and sSFR in Fig. \ref{fig:sSFR}, except in the smallest distance 
bin.  The linear fits quantify this observation --- the slopes are on the order 
of 10$^{-3}$.  Within a distance of 0.05 \hMpc or 0.1$r_{vir}$, dwarf galaxies 
tend to have higher sSFRs than at further distances from their nearest neighbor.  
There does not appear to be any relationship between a dwarf galaxy's sSFR and 
its distance to the center of the nearest group in either distance metric.  In 
these distance comparisons, there is a shift towards higher sSFRs in the void 
dwarf galaxies when compared to the wall dwarf galaxies, as has been observed 
before \citep{Rojas05,vonBendaBeckmann08,Moorman15,Beygu16}.

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_OH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_OH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_OH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_OH}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300_group}
    \caption[Metallicity versus distance to nearest neighbor and group]
    {Metallicity versus distance to the nearest galaxy (on the left) and nearest 
    group (on the right).  The top panel shows the metallicity as a function of 
    the sky separation in \hMpc between the target dwarf galaxy and the 
    neighbor, while the bottom panel shows the metallicity as a function of the 
    closest virial neighbor.  Void galaxies are shown in red, while wall 
    galaxies are shown in black and unknown in green.  We have also included the 
    average metallicity for the galaxies after binning by distance, to discern 
    any finer behavior in the relationships.  Linear fits to the void and wall 
    galaxies are shown in orange and blue, respectively.  It is clear that the 
    void dwarf galaxies have higher metallicities than the wall dwarf galaxies.  
    Only the neighbor galaxies at separations less than 0.05 \hMpc or 
    0.1$r_{vir}$ appear to have some affect on the dwarf galaxies' metallicity.  
    When measuring the distance to the nearest group in \hMpc, it appears that 
    the dwarf galaxies have lower metallicities at distances less than 0.1 \hMpc 
    from their nearest group.}
    \label{fig:OH}
\end{figure}

>>>>

% Small-scale environment - what has been done so far?
In conjunction with the large-scale environment, the small-scale environment 
($\sim$1 \hMpc) has also been found to influence a galaxy's evolution.  A 
well-established morphology-density relation exists \citep{Dressler80}, where 
the fraction of late-type galaxies is inversely proportional to the local 
density.  \cite{Ellison09} determined that a galaxy's local environment 
influences a galaxy's evolution more than its large-scale environment.  
Likewise, \cite{Rupke08} concluded that interacting galaxies have suppressed 
metallicities because interactions induce flows of hydrogen.  For galaxies with 
$M_r < -19$, \cite{Park09} found that galaxy interactions out to the virial 
radius of the nearest neighbor influence the evolution of the target galaxy.  
Along with \cite{Park07}, they determine that the large-scale environment has a 
minimal effect on the evolution of a galaxy once the luminosity and morphology 
are taken into account.

@@

We employ two different spatial metrics to determine the best way to locate a 
galaxy's nearest neighbor.  We set a maximum velocity separation of 300 km/s 
between a galaxy and its nearest neighbor to capture the majority of interacting 
galaxies \citep[according to the distribution in peculiar velocity shown in][]
{Hwang10}.  Within a relative velocity $v_{rel} < 300\text{ km/s}$, we use 
either the physically closest galaxy in units of \hMpc or the galaxy within the 
smallest fraction of its virial radius; both these methods are described below 
in further detail.  The two methods result in different neighboring galaxies for 
about 46\% of our dwarf galaxy sample.

@@

A galaxy's redshift is composed of both the expansion of the universe and the 
galaxy's peculiar velocity (its motion relative to the surrounding galaxies and 
environment).  Known as the ``Finger of God'' effect, the peculiar velocity 
causes galaxy groups and clusters to appear extended along the line of sight 
when using redshift as a distance measurement.  When we calculate distances on 
large scales, the peculiar velocity is negligible.  However, when we study the 
distance between two objects in the universe on a small scale (within a few 
\hMpc), the peculiar velocity dominates.  The relative velocity $v_{rel}$ 
between galaxies $a$ and $b$ is defined as
\begin{equation}
    v_{rel} = |z_a - z_b|c
\end{equation}
where $z$ is the redshift.  We require all 
neighbors to have a maximum relative velocity $v_{rel} < 300\text{ km/s}$, as we 
believe those outside this range will have minimal influence on the target 
galaxy's evolution.  We show in Sec. \ref{sec:selection_effects} that our 
results are insensitive to this value.

@@

The distance on the sky between two galaxies is found by projecting the two 
galaxies onto a sphere of radius $\bar{r}$, where $\bar{r}$ is the average 
distance from Earth of the two galaxies.  This assumes that two galaxies which 
are gravitationally bound are in a system where the relative velocity between us 
and the system is 0 and that $\bar{r}$ is the distance to the center of the 
system.  For redshifts $z \ll 1$, we can approximate the distance to the system 
as
\begin{equation}
    \bar{r} = \frac{\bar{z}c}{H_0}
\end{equation}
where $\bar{z}$ is the average redshift of the two galaxies, $c$ is the speed of 
light, and $H_0$ is the Hubble constant.  Each galaxy's right ascension (RA) and 
declination (dec.) are converted to Cartesian coordinates to find their sky 
separation.

@@

\cite{Choi07} find that the velocity dispersion of a galaxy depends on its 
morphological type, where $\sqrt{2}\sigma_{late} \approx \sigma_{early}$.  In 
terms of the velocity dispersion, the kinetic energy of a galaxy 
$K = 3/2 \sigma^2$.  Its gravitational potential energy $U = 3GM/5R$.  
Therefore, the virial theorem shows us that
\begin{align}
    3\sigma^2 \simeq \frac{3}{5} \frac{GM}{R}\nonumber \\
    M \simeq \frac{5\sigma^2 R}{G}
\end{align}
With $\gamma \equiv M/L$, at a fixed luminosity and virial radius we see that
\begin{equation}
    \gamma_{late} \simeq \frac{5\sigma_{late}^2 R}{GL} \qquad \gamma_{early} \simeq \frac{5\sigma_{early}^2 R}{GL}
\end{equation}
Taking the ratio of the two mass-to-light ratios and using the relation between 
the velocity dispersions found by \cite{Choi07}, we find that the mass-to-light 
ratio depends on the galaxy's morphological type: 
$\gamma_{early} = 2\gamma_{late}$.

\cite{Hwang10} define $200\rho_c = 740\bar{\rho}$, where 
$\bar{\rho} = (0.0223\pm 0.0005)(\gamma_{late}L_{-20})(\text{\hMpc})^3$.  We can 
then rewrite Eqn. \ref{eqn:r_vir} as
\begin{equation}
    r_{vir} = \left( \frac{3}{4\times 740\times 0.0223\pi} \frac{\gamma}{\gamma_{late}} \frac{L}{L_{-20}} \right)^{1/3}
\end{equation}
where $L_{-20}$ is the luminosity of a galaxy with $M_r = -20$.  We can then use 
the virial radius to scale the distance between two galaxies as a fraction of 
the neighbor's virial radius.

@@

% SDSS
%The Sloan Digital Sky Survey Data Release 7 \citep[SDSS DR7;][]{Abazajian09} is 
%a wide-field multiband imaging and spectroscopic survey which maps approximately 
%one-quarter of the northern sky using a drift scanning technique.  Photometric 
%data in the five-band SDSS system --- $u$, $g$, $r$, $i$, and $z$ --- is taken 
%on a dedicated 2.5m telescope at the Apache Point Observatory in New Mexico 
%\citep{Fukugita96,Gunn98}.  Galaxies with Petrosian $r$-band magnitudes 
%$m_r < 17.77$ are selected for follow-up spectroscopic analysis \citep{Lupton01,
%Strauss02}.  The galaxy colors are taken from the Korean Institute for Advanced 
%Study Value-Added Galaxy Catalog \citep[KIAS-VAGC;][]{Choi10}, which contains 
%galaxies from the SDSS DR7 main sky survey based on the New York University 
%Value-Added Galaxy Catalog Data Release 7 \citep[NYU-VAGC;][]{Blanton05}.  Total 
%star formation rates (SFR) and total specific star formation rates (sSFR) are 
%from the MPA-JHU value-added catalog\footnote{Available at 
%\url{http://www.mpa-garching.mpg.de/SDSS/DR7/}}, calculated using the technique 
%described in \cite{Brinchmann04}.  
The gas-phase chemical abundances used are from \cite{Douglass17c}, which are 
calculated using the Direct $T_e$ method.  The galaxies' large-scale 
environments are based on the void catalog compiled by \cite{Pan12}, which is 
constructed from SDSS DR7 using the VoidFinder algorithm of \cite{Hoyle02}.  
Galaxies that are located within identified voids are labeled as void galaxies, 
and those that do not fall within a void are designated as wall galaxies.  The 
large-scale environment within 5 \hMpc of the edge of the main SDSS DR7 
footprint cannot be described using the VoidFinder algorithm because the minimum 
diameter of a void is 10 \hMpc.  Therefore, the large-scale environment for 
galaxies within 5 \hMpc of the edge of the main footprint in SDSS DR7 is 
designated as unknown.

@@

Two galaxy samples are used in this analysis.  The largest one contains the 
11,002 dwarf galaxies spectroscopically observed in SDSS DR7.  The second sample 
contains those star-forming dwarf galaxies from the first set that have 
gas-phase chemical abundances in \cite{Douglass17c}, totaling 1920 dwarf 
galaxies.  Because this subset of galaxies contains only star-forming galaxies 
and is not representative of all dwarf galaxies, we show in Section 
\ref{sec:selection_effects} that this selection effect may affect our results.

@@

In addition to comparing the target galaxies to their nearest neighbor, we also 
look at the relationship between the dwarf galaxies' properties and their 
proximity to the nearest galaxy group.  We use the \emph{Mr18} Berlind group 
catalog \citep{Berlind06} as our source of groups, which is built on the 
galaxies in the NYU-VAGC. The catalog identifies groups using a 
friends-of-friends algorithm \citep{Huchra82} to connect galaxies with 
$M_r < -18$.

@@

The relationships between various physical parameters and the distance to the 
nearest neighbor or group for our sample of star-forming dwarf galaxies are 
shown in Figs. \ref{fig:ur}--\ref{fig:NO}.  In each of the four plots within 
each figure, we bin the galaxies in distance-space and show the median parameter 
value in each bin, to discern any overall trends in the data.  We apply a linear 
regression to the data; the output of these fits are in Table \ref{tab:fits}.  
Each of these four plots probes the distance relationship from a different 
angle.  The top left plots in Figs. \ref{fig:ur}--\ref{fig:NO} relate the target 
dwarf galaxy's parameter to the distance to its nearest neighbor, as defined by 
the closest galaxy on the sky in \hMpc with a velocity difference less than 300 
km/s.  The bottom left plots relate the target dwarf galaxy's parameter to the 
distance to its nearest neighbor, as defined by the closest galaxy on the sky in 
units of the virial radius of the neighbor galaxy with a velocity difference 
less than 300 km/s.  The nearest galaxy is not necessarily the same for these 
two distance measurements, as explained in Sec. \ref{sec:Theory_dist}.

We repeat this same analysis on the nearest group to the target dwarf galaxy.  
The top right plots in Figs. \ref{fig:ur}--\ref{fig:NO} relate the target dwarf 
galaxy's parameter to the distance to the center of the nearest group, as 
defined as the closest group in the sky in \hMpc with a velocity difference less 
than 300 km/s.  The bottom right plots in Figs. \ref{fig:ur}--\ref{fig:NO} 
relate the target dwarf galaxy's parameter to the distance to the nearest group 
as defined by the closest group on the sky in units of the group's rms radius 
with a velocity difference of less than 300 km/s.  Groups are very rare in voids 
(by nature of the void environment), so the uncertainty in the binned values 
shown in these plots is much larger than in the galaxy neighbor plots.

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_ur}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_ur}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_ur_300_group}
    \caption[$u-r$ versus distance to nearest neighbor and group]{Color ($u-r$) 
    versus distance to the nearest galaxy (on the left) and nearest group (on 
    the right).  The top panels show the color as a function of the sky 
    separation in \hMpc between the target dwarf galaxy and the neighbor, while 
    the bottom panels show the color as a function of the closest virial 
    neighbor.  Void galaxies are shown in red, while wall galaxies are shown in 
    black and unknown in green.  We have also included the median color for the 
    galaxies after binning by distance, to discern any finer behavior in the 
    relationships.  Linear fits to the void and wall galaxies are shown in 
    orange and blue, respectively.  It is clear that the void dwarf galaxies are 
    bluer than the wall dwarf galaxies.  The nearest galaxies appear to only 
    have some affect on the dwarf galaxy's color at separations less than 0.05 
    \hMpc, or 0.1$r_{vir}$ (for wall galaxies; 0.2$r_{vir}$ for void galaxies).  
    There appears to be no relationship between a dwarf galaxy's color and its 
    distance to the nearest group.}
    \label{fig:ur}
\end{figure}

Because of the known morphology-density relation, we expect to find that a dwarf 
galaxy's color becomes bluer as the distance to the nearest group increases, but 
we expect the dwarf galaxy's color to become bluer as the distance to the 
neighboring galaxy decreases.  Fig. \ref{fig:ur} shows very little relationship 
between the distance and color, except in the smallest distance bin.  The linear 
fits quantify this observation --- the slopes are on the order of 10$^{-3}$.  
However, within a distance of 0.05 \hMpc or 0.1$r_{vir}$ (for wall galaxies; 
0.2$r_{vir}$ for void galaxies), dwarf galaxies tend to be bluer than at further 
distances from their nearest neighbor.  There does not appear to be any 
relationship between a dwarf galaxy's color and its distance to the center of 
the nearest group.  It has been well-established that void galaxies tend to be 
bluer than galaxies in denser environments \citep{Grogin99,Rojas04,Patiri06,
vonBendaBeckmann08,Hoyle12}; this shift is apparent in Fig. \ref{fig:ur}, where 
the void dwarf galaxies are slightly bluer than the wall dwarf galaxies at all 
distances.

\subsubsection{Specific star formation rate}

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_sSFR}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_sSFR}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_sSFR}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_sSFR}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_sSFR_300_group}
    \caption[sSFR versus distance to nearest neighbor and group]{sSFR versus 
    distance to the nearest galaxy (on the left) and nearest group (on the 
    right).  The top panels show the sSFR as a function of the sky separation in 
    \hMpc between the target dwarf galaxy and the neighbor, while the bottom 
    panels show the sSFR as a function of the closest virial neighbor.  Void 
    galaxies are shown in red, while wall galaxies are shown in black and 
    unknown in green.  We have also included the median sSFR for the galaxies 
    after binning by distance, to discern any finer behavior in the 
    relationships.  Linear fits to the void and wall galaxies are shown in 
    orange and blue, respectively.  It is clear that the void dwarf galaxies 
    have higher sSFRs than the wall dwarf galaxies.  Only the neighbor galaxies 
    at separations less than 0.05 \hMpc or 0.1$r_{vir}$ (for wall galaxies; 
    0.2$r_{vir}$ for void galaxies) appear to have some affect on the dwarf 
    galaxies' sSFR.  There appears to be no relationship between a dwarf 
    galaxy's sSFR and its distance to the nearest group.}
    \label{fig:sSFR}
\end{figure}

Following our prediction for the color-distance relations, we expect the 
specific star formation rate (sSFR) to decrease with distance from the nearest 
neighbor and increase with distance from the nearest group.  We also see very 
little relationship between the distance and sSFR in Fig. \ref{fig:sSFR}, except 
in the smallest distance bin.  The linear fits quantify this observation --- the 
slopes are on the order of 10$^{-3}$.  Within a distance of 0.05 \hMpc or 
0.1$r_{vir}$ (for wall galaxies; 0.2$r_{vir}$ for void galaxies), dwarf galaxies 
tend to have higher sSFRs than at further distances from their nearest neighbor.  
There does not appear to be any relationship between a dwarf galaxy's sSFR and 
its distance to the center of the nearest group in either distance metric.  In 
these distance comparisons, there is a shift towards higher sSFRs in the void 
dwarf galaxies when compared to the wall dwarf galaxies, as has been previously 
observed \citep{Rojas05,vonBendaBeckmann08,Moorman15,Beygu16}.

@@

\begin{figure}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_absDist_OH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupAbsDist_OH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_virDist_OH}
    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/1sig_dwarf_I06relations_groupRDist_OH}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300}
%    \includegraphics[width=0.49\textwidth]{Images/smallScaleEnvironment/dwarf_OH_300_group}
    \caption[Metallicity versus distance to nearest neighbor and group]
    {Metallicity versus distance to the nearest galaxy (on the left) and nearest 
    group (on the right).  The top panels show the metallicity as a function of 
    the sky separation in \hMpc between the target dwarf galaxy and the 
    neighbor, while the bottom panels show the metallicity as a function of the 
    closest virial neighbor.  Void galaxies are shown in red, while wall 
    galaxies are shown in black and unknown in green.  We have also included the 
    median metallicity for the galaxies after binning by distance, to discern 
    any finer behavior in the relationships.  Linear fits to the void and wall 
    galaxies are shown in orange and blue, respectively.  It is clear that the 
    void dwarf galaxies have higher metallicities than the wall dwarf galaxies.  
    Only the neighbor galaxies at separations less than 0.15 \hMpc appear to 
    have some affect on the dwarf galaxies' metallicity.  When measuring the 
    distance to the nearest group in \hMpc, it appears that the dwarf galaxies 
    have lower metallicities at distances less than 0.05 \hMpc from their 
    nearest group.}
    \label{fig:OH}
\end{figure}

Based on our hypothesis that galaxies would be bluer and have higher sSFRs at 
small distances to their nearest neighbors, we anticipate that the metallicity 
of the galaxies would decrease with increasing distance.  As before, we only see 
a relationship between the distance and metallicity in the smallest distance 
bins in Fig. \ref{fig:OH}.  The linear fits quantify this observation --- the 
slopes are on the order of 10$^{-3}$.  Within a distance of 0.15 \hMpc, dwarf 
galaxies tend to have higher metallicities than at further distances from their 
nearest neighbor.  At distances less than 0.05 \hMpc from the center of the 
nearest group, dwarf galaxies might have lower than average metallicities.  
However, this could be an erroneous conclusion due to small-number statistics.  
In these distance comparisons, there is a shift towards higher metallicities in 
the void dwarf galaxies when compared to the wall dwarf galaxies, as has been 
observed by \cite{Douglass17b} and \cite{Douglass17c}.
